The hidden manifold distance for functional data

### 2019-08-22 index.Rmd
rmarkdown outputs to body

---
title: "The hidden manifold distance for functional data"
output:
  html_document:
    df_print: paged
    number_sections: yes
  word_document: default
  pdf_document:
    keep_tex: yes
    number_sections: yes
bibliography: references.bib
---

@@

## Results
???Still need to describe parameters under study: SNR, denseness of observations ($K_{observed}$). Describe parameters that are fixed:  $K_smooth$ and com_grid. Describe tuning parameters for our method: $s$ and $h$.

```{r, engine = 'bash', eval = FALSE}
sbatch compare_methods.sh
```

```{r, eval=FALSE}
R cluster_results.R
```
<!--

>>>>

---
title: "The hidden manifold distance for functional data"
output: 
  html_document:
    fig_caption: true
bibliography: references.bib
---

```{r, include=FALSE}
source("cluster_results.R",echo=FALSE)
```

@@

## Results

???Still need to describe parameters under study: SNR, denseness of observations ($K_{observed}$). Describe parameters that are fixed:  $K_smooth$ and com_grid. Describe tuning parameters for our method: $s$ and $h$.

```{r, engine = 'bash', eval = FALSE, include=FALSE}
sbatch compare_methods.sh
scp susanwei@spartan.hpc.unimelb.edu.au:/home/susanwei/functional_manifold_data/taskid* /Documents/Githuib/functional_manifold_data/
```

```{r, echo=FALSE, eval=TRUE, results='hide'}

setwd("./sim_results")

method_names=c("SS","s=1","s=2","s=3","L2")
nr_methods = length(method_names)

combination_res_assess<- cbind(rep(1:nr_methods,3),rep(1:3,each=nr_methods)) # nr_methods*3 combinations of methods and assesment measures
# TODO: fix hardcoding
combination_para <- expand.grid(c(5,2,4),c(0.5),c(30)) # combinations of the parameters, copied from compare_methods.R

apply(combination_para,1,create_boxplot,mat_ind=combination_res_assess,method_names=method_names,nr_methods=nr_methods)

setwd("../")
```

\begin{figure}
\includegraphics{sim_results/sce=5_SNR=high_Kobs=30}
\caption{blah}
\end{figure}

<!--
